A Low-cost Natural Interaction based on a Camera Hand-Gestures Recognizer

### 2011-02-01 paper.tex
Thomas rmsq

\begin{abstract}
The search for new simplified interaction techniques is always treated as a
manner to advance the communication with interactive devices.
In this paper we present our work to generate interactive TVs modules capable of
recognizing human gestures through a low-cost camera.
We recognize gestures by the tracking of human skin blobs and analyzing the 
corresponding movements to control a TV in an ubiquitous computing environment.
Then we present a new gesture library generated after an analysis of TV's Talk-shows.

@@

\subsection{Gestures taxonomies}
By looking in the possible gestures human can generate \cite{Gesturecraft}, we
get a huge amount of possibilities so there is a need for a taxonomy.
%Many possible taxonomies exist according to the technical or analytical aspects:
In order to describe and analyse each gesture, we can rely on the following
aspects:
\begin{description}
 \item[Gesture Creation Space:] We use this criteria to distinguish between gestures made in the 2D or 3D space.
 \item[Number of used strokes:] We use this criteria to distinguish between gestures constructed by only one path and between those using many paths, so the recognition needs to wait for all strokes before the recognition
 \item[Gesture use:] We use this criteria to distinguish gesture based on the specific use of it, gestures for disabled people, gestures in talk-shows, gestures in meetings.
% \item[]
% \item[]
\end{description}
%Gesture and Thoughts, page 18
According to McNail \cite{gestureThought}, it is possible and useful to
distinguish between these gestures:
\begin{description}
 \item[Gesticulation] is motion that embodies a meaning reliable to the
accompanying speech. It is made chiefly with the arms and hands but is not
restricted to these body parts.
 \item[Speech-linked gestures] are parts of sentences themselves, the gesture
completes the sentence structure.
 \item[Emblems] are conventionalized signs, such as thumbs-up or the ring (first
finger and thumb tips touching, other fingers extended) for ``OK.''
 \item[Pantomime] is dumb show, a gesture or sequence of gestures conveying a
narrative line, with a story to tell, produced without speech.
\end{description}

@@

The figure\ref{handg} shows our supported gestures. We provide a movement mode
used to select directions, then a command mode, then a hand fingers recognition,
and in the end a cursor movement mode.
\pagebreak 
We have selected to support 4 basic gestures to be extended depending on the
context fulfilling the requirements of a benchmark scenario.

@@

\subsection{Used Materials}
We have chosen a low-cost camera for our work to be able to integrate it with other components in the future.
The PS3Eye camera matched our expectations with a 640x480 resolution combined with a 60 frames-per-second capability.
This camera costs about 40\$ which is a reasonable price for a potential market deployment.

@@

\subsection{Color Transformations}
The video processing is based on several modules. First, a basic but adaptive skin color segmentation of a large interval of human skin varieties is performed \cite{skinColorSeg}.
We do an histogram tuning to better enlarge the colors to all the space available.
Then we transform the color space from BGR to YCrCb because it’s the one with the less parameters where we can do easy segmentation. The transformation from these two color spaces is chosen also because it’s linear \cite{skinColorSeg}.

@@

\subsection{Input Filtering}
Then, a morphological kernel is applied to smooth the results, this is necessary
to clean the image from lonely pixels and holes inside skin zones.
Each blob is labeled in linear time we use the algorithm \cite{CompLabeling} , which requires 1 to 4 passes to recognize all blobs with their bounding path.
We identify the hands and the head by a calibration focused on their first position in the screen. We identify them and add a tag to their respective blobs.

\subsection{Blobs Detection}
After having the hand and head blobs identified, an efficient tracking method based on the occlusion is used. It re-triggers a phase of calibration when losing the logic of tracking.
A bounding box distant measure similar to that found in the paper \cite{app06} ("distantBlobTrack"). A distance matrix is also used ('Proximity matrix calculation and "used blob" list initialization') like the one explained in the paper. 
\ignore{
When the matrix of distance is set up, there are some loops:
* A loop for detect inactive tracks: those tracks with no blobs near.
* Detect and create new tracks: those blobs without a track near.
* A loop to assign blobs to tracks. It makes clusters with blobs that are close and assign them to a track. In this step some tracks could merge in one.
* At the end, all inactive tracks are checked to delete the old ones.
}
To better handle blobs, the bounding path of the blobs is simplified to a set of few points when needed, this is used to identify picks for the counter mode.

@@

\section{Gestural informations and Recognition modes}
The output of this video processing is the input of the recognition module, which is based on the blob location on the screen. Four different modes are defined according to the hand locations and the switch between them is based on the grammar:

>>>>

\begin{abstract}
The search for new simplified interaction techniques is always treated as a
manner to advance the communication with interactive devices.
In this paper, we present our work to generate interactive TVs modules capable of
recognizing human gestures through a low-cost camera.
We recognize gestures by the tracking of human skin blobs and analyzing the 
corresponding movements to control a TV in an ubiquitous computing environment.
Then, we present a new gesture library generated after an analysis of TV's Talk-shows.

@@

\subsection{Gestures taxonomies}
By looking at the possible gestures human can generate \cite{Gesturecraft}, we
get a huge amount of possibilities. So, there is a need for a taxonomy.
%Many possible taxonomies exist according to the technical or analytical aspects:
In order to describe and analyse each gesture, we can rely on the following
aspects:
\begin{description}
 \item[Gesture Creation Space:] We use this criteria to distinguish between gestures made in the 2D or 3D space.
 \item[Number of used strokes:] We use this criteria to distinguish between gestures constructed by only one path and between those using many paths, so the recognition needs to wait for all strokes before the recognition
 \item[Gesture use:] We use this criteria to distinguish gesture based on the specific use of it, gestures for disabled people, gestures in talk-shows, gestures in meetings.
% \item[]
% \item[]
\end{description}
%Gesture and Thoughts, page 18
According to McNail \cite{gestureThought}, it is possible and useful to
distinguish between these gestures:
\begin{description}
 \item[Gesticulation] is a motion that embodies a meaning reliable to the
accompanying speech. It is made chiefly with the arms and hands but is not
restricted to these body parts.
 \item[Speech-linked gestures] are parts of sentences themselves, the gesture
completes the sentence structure.
 \item[Emblems] are conventionalized signs, such as thumbs-up or the ring (first
finger and thumb tips touching, other fingers extended) for ``OK.''
 \item[Pantomime] is dumb show, a gesture or sequence of gestures conveying a
narrative line, with a story to tell, produced without speech.
\end{description}

@@

Figure\ref{handg} shows our supported gestures. We provide a movement mode
used to select directions, then a command mode, then a hand fingers recognition,
and, finally, a cursor movement mode.
\pagebreak 
We have selected to support 4 basic gestures to be extended depending on the
context fulfilling the requirements of a benchmark scenario.

@@

\subsection{Used Materials}
We have chosen a low-cost camera for our work that can be integrated with other components in the future.
The PS3Eye camera matched our expectations with a 640x480 resolution combined with a 60 frames-per-second capability.
This camera costs about 40\$, which is a reasonable price for a potential market deployment.

@@

\subsection{Color Transformations}
The video processing is based on several modules. First, a basic but adaptive skin color segmentation of a large interval of human skin varieties is performed \cite{skinColorSeg}.
We also use a histogram equalisation technique to better enlarge the colors to all the space available.
Then we transform the color space from BGR to YCrCb, as it’s the most adapted one to skin segmentation
Moreover, the corresponding transformation is linear \cite{skinColorSeg}.

@@

\subsection{Input Filtering}
During the next step, a morphological kernel is applied to smooth the results, this is necessary
to clean the image from isolated pixels and holes inside skin zones.
Each blob is labeled in linear time using the algorithm described in \cite{CompLabeling} , which requires 1 to 4 passes to recognize all blobs with their bounding path.
We identify the hands and the head by a calibration focused on their first position in the screen. We identify them and add a tag to their respective blobs.

\subsection{Blobs Detection}
After having the hand and head blobs identified, an efficient tracking method based on the occlusion is used. It re-triggers a phase of calibration when losing the logic of tracking.
A bounding box distant measure similar to that found in the paper \cite{app06} ("distantBlobTrack"). A distance matrix is also used ('Proximity matrix calculation and "used blob" list initialization') like the one explained in the paper. 
\ignore{
When the matrix of distance is set up, there are some loops:
* A loop for detect inactive tracks: those tracks with no blobs near.
* Detect and create new tracks: those blobs without a track near.
* A loop to assign blobs to tracks. It makes clusters with blobs that are close and assign them to a track. In this step some tracks could merge in one.
* At the end, all inactive tracks are checked to delete the old ones.
}
To better handle blobs, the bounding path of the blobs is simplified to a set of few points when needed. This is used to identify picks for the counter mode.

@@

\section{Gestural informations and Recognition modes}
The output of this video processing is the input of the recognition module, which is based on the blob location on the screen. Four different modes are defined according to the hand locations. The switch between them is based on the following grammar:
